Predicting Erectile Function in Patients Undergoing Stereotactic Body Radiation Therapy

### 2017-01-26 paper_draft.Rmd
spellcheck
fixed count table

## Methods
Clinical and biomarker data were collected from 325 patients with prostate cancer that experienced SBRT and were followed for 2 years or longer between 2008 and 2013. All the patients in the data were treated at a single institution. The dataset does not have any missing values, but only contains information from patients who underwent radiation therapy. These radiation therapy patients are generally older, sicker, and at more advanced stages of cancer than patients who elect for surgery. The dataset also contains information from patients who already reported no erectile function at baseline, and these patients were not removed before analysis.

@@

## Results
```{r load_packages, message=FALSE, warning=FALSE, results='hide', echo=FALSE}
# Load packages
library(readxl)
library(knitr)
library(data.table)
library(corrplot)
library(broom)
library(stargazer)
library(ggplot2)
library(gridExtra)
library(psych)
library(ROCR)
```
```{r load_data, message=FALSE, warning=FALSE, results="hide", echo = F}
prostate <- read_excel("~/Downloads/Prostate SBRT Sexual Function Data.xlsx", skip = 7)
prostate <- data.table(prostate)
prostate <- prostate[complete.cases(prostate)] # remove last row which is empty
# Code ADT as numeric; Y = 1, N = 0
prostate[ADT == "Y", ADT := 1]
prostate[ADT == "N", ADT := 0]
prostate[, ADT := as.numeric(ADT)]
```

@@

```{r freq_table, echo = F, results="asis"}
stargazer(table(prostate[, .(`Erectile Function at Baseline`, `Erectile Function at 2 years`)]), header = F)
```

@@

## Appendix

>>>>

## Methods
Clinical and biomarker data were collected from 325 patients with prostate cancer that experienced SBRT and were followed for 2 years or longer between 2008 and 2013. All the patients in the data were treated at a single institution. The dataset does not have any missing values, but only contains information from patients who underwent radiation therapy. These radiation therapy patients are generally older, sicker, and at more advanced stages of cancer than patients who elect for surgery. The dataset also contains information from patients who already reported no erectile function at baseline, and these patients were not removed before analysis. Table 2 contains counts of patients by erectile function at baseline and at two years.

@@

## Results
```{r load_packages, message=FALSE, warning=FALSE, results='hide', echo=FALSE}
# Load packages
library(readxl)
library(knitr)
library(data.table)
library(corrplot)
library(broom)
library(stargazer)
library(ggplot2)
library(gridExtra)
library(psych)
library(ROCR)
library(xtable)
```
```{r load_data, message=FALSE, warning=FALSE, results="hide", echo = F}
prostate <- read_excel("~/Downloads/Prostate SBRT Sexual Function Data.xlsx", skip = 7)
prostate <- data.table(prostate)
prostate <- prostate[complete.cases(prostate)] # remove last row which is empty
# Code ADT as numeric; Y = 1, N = 0
prostate[ADT == "Y", ADT := 1]
prostate[ADT == "N", ADT := 0]
prostate[, ADT := as.numeric(ADT)]
```

@@

```{r freq_table, echo = F, results="hide"}
# stargazer(table(prostate[, .(`Erectile Function at Baseline`, `Erectile Function at 2 years`)]), header = F, title = "Counts by erectile function", column.labels = c("Baseline","Two years"), dep.var.labels = c("Baseline","Two years"))
```
\begin{table}[!htbp] \centering 
  \caption{Counts by erectile function} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} cccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & Baseline & Two years & Count \\ 
\hline \\[-1.8ex] 
1 & 0 & 0 & $153$ \\ 
2 & 1 & 0 & $70$ \\ 
3 & 0 & 1 & $14$ \\ 
4 & 1 & 1 & $88$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@
